---
title: "3.0.1missing"
author: "Huize Zhang"
date: "15/04/2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

library(tidyverse)
library(visdat)
library(gridExtra)
library(forecast)
library(naniar)

load("raw_data/court.rda")
load("raw_data/au.rda")
```

```{r missing_summary}
missing <- court %>% 
  select(judge_id, frame_id, video_id, x_1) %>% 
  mutate(judge_id = as.factor(judge_id)) %>% 
  group_by(video_id, judge_id) %>% 
  summarise(na_count = sum(is.na(x_1)), 
            count = n(),
            na_prop = na_count/count, 
            data_prop = 1-na_prop)

# data related to judge Gordon is removed because four out of five cases with Gordon has missing proportion greater than 99% 

missing %>% filter(judge_id == "Gordon")

# One cases from Kiefel is also removed because of na_prop ==1
missing %>% filter(na_prop ==1)
```

```{r}
miss_var_table(au) # four variables don't have missings: judge_id, vido_id, frame_id, speakers, all others have missing

miss_case_table(au) # 1768 cases don't have missings while the other 2833 cases all have 35 missings in the case. 

# Thus the missing structure: An observation is either missing for all the variables or has non-missing
```



# Missing Imputation

The missing mechanism in our case is a unit-level missing as the missingness depends on other unobservables. For example, the missingness could be due to the fact that a judge is reading the materials on the desk so the face is not captured for a particular frame or simply because some faces are not detectable for the given resolution of the video stream. However, since that data is in time series structure, simply drop the missing observation will cause the time interval to be irregular and complicate further analysis. Thus proper imputation method is needed. Because there is no obvious trend or seasonality in each action unit series, imputation methods using time series models will not be suitable in our case.  Therefore, we choose the linear interpolation(`na.interp`) from the `forecast` package to impute the missing value for each action unit. Notice that the funtion requires at least two non-NA points in a series, we drop 4 video-judge pairs where no data is available for a particular judge in a particular case, namely (OKS, Gordon), (Parkes, Gordon), (Rinehart_b, Gordon) and (Rinehart_b, Kiefel). 

We simply drop Judge Gordon - only one video case. 

```{r missing_imputation}
au_intensity <- au %>% 
  filter(judge_id %in% c("Keane", "Nettle", "Edelman", "Gageler", "Bell")|
           (judge_id == "Kiefel" & video_id != "Rinehart_b")) %>% 
  select(frame_id, judge_id, video_id, ends_with("_r")) %>% 
  gather(AU, value, -c(frame_id: video_id)) %>% 
  group_by(judge_id, video_id, AU) %>% 
  nest() %>% 
  mutate(interp = map(data, 
                      ~.x %>% pull(value) %>% na.interp %>% as.numeric)) %>% 
  select(judge_id, video_id, AU, interp) %>% 
  unnest() %>% 
  group_by(judge_id, video_id, AU) %>%
  mutate(frame_id = row_number()) %>% # add back frame_id as index
  spread(AU, interp) %>% 
  left_join(au %>% select(judge_id: speaker)) # add back speaker column
```

Binomial imputation function 
```{r}
binomial_imputation <- function(x){
  
  # calculate the probability of 1 and 0 and count of NA 
  percent <- x %>% 
    add_count(value) %>% 
    mutate(percent = n/length(value)) %>% 
    distinct(value,n,percent) %>% 
    gather(measure, num, c(n, percent)) %>% 
    spread(value, num)
  
# sample from binomial distribution  
  if("<NA>" %in% colnames(percent)){
     if ("1" %in% colnames(percent)){
       if("0" %in% colnames(percent)){
        percent <- percent %>% as.matrix()
        imputation <- sample(c(0,1), percent[1,4], prob = percent[2,2:3], replace = TRUE)
        }else{
          # if no col is 0, all the value is 1, impute 1
          percent <- percent %>% as.matrix()
          imputation <- rep(1, percent[1,3])
        }
      }else{
        # if no col is 1, all the value is 0, impute 0
        percent <- percent %>% as.matrix()
        imputation <- rep(0, percent[1,3])
      }
  }else{
      imputation = NULL
    }
  
  if(sum(is.na(x$value)) ==0){
    impute <- x %>% 
      as_tibble() %>% 
      select(value)
    
    return(impute)
    
  }else{
      impute <- x %>% 
        filter(is.na(value)) %>% 
        mutate(impute = imputation) %>% 
        select(-value) %>% 
        right_join(x, by = "frame_id") %>% 
        mutate(value = ifelse(is.na(impute), value, impute)) %>% 
        as_tibble() %>% 
        select(value)
      
      return(impute)
  }
}

```

```{r}
# imputation from a binomial distribution
au_presence <- au %>% 
  filter(judge_id %in% c("Keane", "Nettle", "Edelman", "Gageler", "Bell")|
           (judge_id == "Kiefel" & video_id != "Rinehart_b")) %>% 
  select(frame_id, judge_id, video_id, ends_with("_c")) %>% 
  gather(AU, value, -c(frame_id: video_id)) %>% 
  group_by(judge_id, video_id, AU) %>%
  nest() %>% 
  mutate(impute = map(data, binomial_imputation)) %>% 
  select(judge_id, video_id, AU, impute) %>% 
  unnest() %>% 
  group_by(judge_id, video_id, AU) %>% 
  mutate(frame_id = row_number()) %>% # add back frame_id as index
  spread(AU, value) %>% 
  left_join(au %>% select(judge_id: speaker)) # add back speaker column

au_imputed_old <- au_intensity %>% 
  left_join(au_presence, 
            by = c("judge_id", "video_id", "frame_id", "speaker")) 

save(au_imputed_old, file = "raw_data/au_imputed_old.rda") 

au_imputed <- au_imputed_old %>% 
  group_by(judge_id) %>% 
  gather(AU_label, value, -c(judge_id, video_id, frame_id, speaker)) %>% 
  separate(AU_label, c("AU", "suffix")) %>% 
  spread(suffix, value) %>% 
  rename(presence = c, intensity = r) 

save(au_imputed, file = "raw_data/au_imputed.rda") 
```

# Data quality

There is a problem with the data: for some records, the intensity score is high but presence ==0, see below

```{r}  
au_imputed %>% 
  filter(presence ==0) %>% 
  arrange(desc(intensity)) 
```

Our imputation could be a reason for this to happen(impute intensity via linear interpolation and presence from random sample - they are done independently), However, the original data also has this problem(see below). 

```{r}
au %>% 
  group_by(judge_id) %>% 
  select(-c(speaker)) %>% 
  gather(AU_label, value, -c(judge_id, video_id, frame_id)) %>% 
  separate(AU_label, c("AU", "suffix")) %>% 
  spread(suffix, value) %>% 
  rename(presence = c, intensity = r) %>%  
  filter(presence == 0) %>% 
  arrange(desc(intensity))
```

so we will have to adjust for the presence value if the intensity is higher than the threshold we set, say intensity >= 1 

```{r}
au_tidy <- au_imputed %>% 
  mutate(presence = case_when(
    presence ==1 ~ presence, 
    presence ==0 & intensity >=1 ~ 1, 
    presence ==0 & intensity <1 ~ 0, 
  )) %>% 
  ungroup() %>% 
  mutate(judge_id = as.factor(judge_id), 
         speaker = as.factor(speaker), 
         AU = as.factor(AU))

save(au_tidy, file = "raw_data/au_tidy.rda")
```

