---
title: "4.2Normal/Abnormal"
author: "Huize Zhang"
date: "27/06/2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,message = FALSE)

library(tidyverse)
library(boot)

load("raw_data/au_imputed.rda")
```

simulation for 

- each au as a bernouilli 
- compute the mean from the data (aggregate at all level)
- simulate n = 1000 to get the variation 
- plot errorbarplot 
- find the points outside the error bar for each judge see outliners

```{r sample_size}
count_video_sample <- function(dt){
  dt %>% 
    select(frame_id, video_id, speaker) %>% 
    group_by(video_id, speaker) %>% 
    summarise(count = n()) %>% 
    spread(speaker, count) %>% 
    rowwise() %>% 
    mutate(Total = sum(Appellent + Respondent))
}

judge_id <-  list("Bell","Keane","Kiefel","Gageler","Nettle","Edelman")

df <- map(judge_id, function(judge){
  a <- au_imputed %>% 
    filter(judge_id == judge) %>% 
    count_video_sample() %>% 
    filter(Total > 10)
  })

names(df) <- judge_id

sample_size <- bind_rows(df,.id = "id") %>% 
  as_tibble() %>% 
  rename(judge_id = id)

```

# Simulation study 
This markdown file contains information on the simulation study for the presence of an action unit. see `4.2.2CI_intensity` for the study on the intensity of the action unit. 

```{r}
# average time an action unit appears for a judge 
au_aggregate <- au_imputed %>% 
 group_by(judge_id) %>%
 right_join(sample_size) %>%
 summarise_at(vars(AU01_c: AU45_c), .funs = mean) %>%
 gather(AU, mean_agg, -judge_id)

# au_video provides more information on the average appearance of an action unit on the video level
au_video <- au_imputed %>%
 select(AU01_c: AU45_c, judge_id: speaker) %>%
 group_by(judge_id, video_id) %>%
 summarise_at(vars(AU01_c: AU45_c), mean) %>%
 gather(AU, mean_ind, -judge_id, -video_id) %>%
 right_join(sample_size)

count <- au_imputed  %>%
 select(AU01_c: AU45_c, judge_id: speaker) %>%
 group_by(judge_id) %>%
 right_join(sample_size) %>%
 summarise(count = n())

save(au_aggregate, file = "raw_data/au_aggregate.rda")
save(au_video, file = "raw_data/au_video.rda")
save(count, file = "raw_data/count.rda")
```

## simulation function using binomial distribution
```{r}
sim_norm <- function(count, mean_true, M = 1000){
 mean <- numeric(length = M)
 
 for (i in seq_len(M)){
   sim <- rbinom(count, 1, mean_true)
   mean[i] <- mean(sim)
 }
 
 mean_sorted <- sort(mean)
 sim_mean <- mean_sorted[500] # maybe try to use qnorm()
 sim_ci_low <- mean_sorted[25]
 sim_ci_high <- mean_sorted[975]
 return(list(sim_mean = sim_mean,
             sim_ci_low = sim_ci_low,
             sim_ci_high = sim_ci_high))
}
```


### simulation using binomial distribution 

- The interval is quite small: a lot of the action units are out of the simulation bound - what to do with them?
- It seems that the simulation from the two methods are not consistent - bootstraping has much wider confidence interval 


notes:
- simulation result doesnt differentiate from M = 100, 1000, 10000

```{r eval = FALSE}
# For majority: simulate from a binomial distribution - for Bell and Gordon, because e number of sample for each vidoe is too small so we do bootstrap interval seperately

au_sim_majority <- au_aggregate %>%
 left_join(count) %>%
 filter(judge_id != "Bell", judge_id != "Gordon")

temp <- map2_df(.x = au_sim_majority$count, .y = au_sim_majority$mean_agg,
    function(x, y) sim_norm(x, y))

au_sim2_majority <- au_sim_majority %>%
 bind_cols(temp) %>%
 left_join(au_video, by = c("judge_id", "AU")) %>%
 ungroup() %>%
 mutate(outliers = as.factor(ifelse(mean_ind > sim_ci_low,
                                     ifelse(mean_ind < sim_ci_high, 0, 1), 1)))

au_sim2_majority %>%
 mutate(AU = as.factor(AU)) %>%
 ggplot(aes(x = mean_agg, 
            y = fct_reorder(AU, mean_agg))) +
  geom_errorbarh(aes(xmin = sim_ci_low, xmax = sim_ci_high), col = "gray") +
  facet_wrap(vars(judge_id)) +
  geom_point(aes(x = mean_ind, col = outliers)) + 
  ylab("AU")
  
ggsave("images/sim_bino_appearance.png")

# half binomial and half bootstrapping
# au_sim_bell <- boot_sim("Bell")
# au_sim_gordon <- boot_sim("Gordon")
# au_sim_bind <- bind_rows(au_sim_bell, au_sim_gordon)
# au_sim_both <- au_aggregate %>%
#  left_join(count) %>%
#  filter(judge_id == "Bell"| judge_id == "Gordon")
# au_sim2_both <- au_sim_both %>%
#  left_join(au_sim_bind, by = c("judge_id", "AU")) %>%
#  left_join(au_video, by = c("judge_id", "AU")) %>%
#  ungroup() %>%
#  mutate(outliners = as.factor(ifelse(mean_ind > sim_ci_low,
#                                      ifelse(mean_ind < sim_ci_high, 0, 1), 1)))
# au_sim2 <- bind_rows(au_sim2_majority, au_sim2_both)


# au_sim2 %>%
#   mutate(AU = as.factor(AU)) %>%
#   ggplot(aes(mean_agg, fct_reorder(AU, mean_agg))) +
#   geom_errorbarh(aes(xmin = sim_ci_low, xmax = sim_ci_high), col = "gray") +
#   facet_wrap(vars(judge_id)) +
#   geom_point(aes(x = mean_ind, y = AU, col = outliners))

```

## simulation function: bootstraping 
```{r}
set.seed(377)
mean.fun <- function(data, index){
  val <- data$value[index]
  return(mean(val))
  }

boot_sim <- function(judge){
  dt <- au_imputed %>%
   filter(judge_id == judge) %>%
   select(frame_id, speaker, ends_with("c")) %>%
   gather(AU, value, -c(judge_id: speaker)) %>%
   group_by(AU)
    
 sim <- map(split(dt,dt$AU), function(x){
   boot_obj <- boot(x, mean.fun, R = 10000)
   ci <- boot.ci(boot_obj, conf = c(0, 0.95), type = "perc")
 })
 
 temp <- map_df(sim, function(x) x$percent)
 
 sim_result <- temp[8, ] %>% gather(AU, sim_low) %>%
   left_join(temp[9, ] %>% gather(AU, sim_mean)) %>%
   left_join(temp[10, ] %>% gather(AU, sim_high))
 
 return(sim_result)
}


# nobody looks like an outliner before aggregated by time 
# abnormal_detection <- function(data,index){
#    val <-  data$mean_ind[index]
#    t = mean(val)
#    val_sub <- val[-which.max(val)]
#    tm = mean(val_sub)
#    return(t-tm)
#  }
# x <- au_video %>% filter( AU == "AU01_c", judge_id == "Keane")
# boot_obj <- boot(x, abnormal_detection, R = 1000)
# a <- boot_obj$t %>% as_tibble()
# a %>% ggplot(aes(x = V1)) + 
#   geom_histogram()
# boot_obj$t %>% hist()

```

### Simulation all using bootstrap
```{r}
sim_result<- map_df(.x = judge_id, 
                    ~boot_sim(.x) %>% mutate(judge_id = .x))

save(sim_result, file = "raw_data/sim_result.rda")

ci_count <- au_aggregate %>% 
  left_join(count) %>% 
  right_join(sim_result, by = c("judge_id", "AU")) %>%
  left_join(au_video, by = c("judge_id", "AU")) %>% 
  ungroup() %>% 
  mutate(outliers = as.factor(ifelse(mean_ind > sim_low, 
                                      ifelse(mean_ind < sim_high, 0, 1), 1)))

save(ci_count,file = "raw_data/ci_count.rda")

ci_count %>%
  mutate(AU = as.factor(AU)) %>% 
  ggplot(aes(x = mean_agg, 
             y = fct_reorder(AU, sim_mean))) + 
  geom_errorbarh(aes(xmin = sim_low, xmax = sim_high), col = "gray") + 
  facet_wrap(vars(judge_id)) + 
  geom_point(aes(x = mean_ind, col = outliers)) + 
  ylab("AU")

ggsave("images/sim_boot_appearance.png")
# bootstrap interval is indeed wider than those simulated from binomial 
```



```{r}
outliers <- ci_count %>% 
  filter(outliers == 1, mean_ind > 0.05) 

outliers %>% 
  ggplot(aes(x = mean_ind, y  =AU)) + 
  geom_point(aes(col = video_id)) + 
  facet_wrap(vars(judge_id), scales = "free_y") + 
  geom_errorbarh(aes(xmin = sim_low, xmax = sim_high), col = "gray")

```


# Outlinear detection - Anomaly detection 

```{r}
# library(broom)
# 
# by_index <- au_imputed %>%
#  select(AU01_c: AU45_c, judge_id: speaker) %>%
#  group_by(judge_id, video_id) %>%
#  summarise_at(vars(AU01_c: AU45_c), mean) %>% 
#  gather(AU, mean_ind, -judge_id, -video_id) %>%
#   group_by(judge_id, AU) %>% 
#   nest()
#   
# anomaly_detection <- function(data,index){
#    val <-  data$mean_ind[index]
#    t = mean(val)
#    val_sub <- val[-which.max(val)]
#    tm = mean(val_sub)
#    return(t-tm)
#  }
#   
# model <- by_index %>% 
#   mutate(bootstrap = map(data, ~boot(.x, anomaly_detection, R= 10000))) %>% 
#   mutate(t = map(bootstrap, ~.x$t))
#   
# anomaly_result <- data.frame(matrix(unlist(model$t), nrow=length(model$t), byrow=T)) %>% 
#   mutate(AU = by_index$AU, judge_id = by_index$judge_id) %>% 
#   gather(t_n, value, -c(AU, judge_id))
# 
# Keane <- anomaly_result %>% 
#   filter(judge_id == "Keane") %>% 
#   ggplot(aes(x = value)) +
#   geom_density() + # bins = 3 works
#   facet_wrap(vars(AU), scales = "free")
# 
# Keane
# 
# 
# a <- anomaly_result %>% filter(judge_id == "Keane", t_n == "X1") 
# a$value %>% hist()
```






