---
title: "4.2Normal/Abnormal"
author: "Huize Zhang"
date: "27/06/2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

simulation for 

- each au as a bernouilli 
- compute the mean from the data (aggregate at all level)
- simulate n = 1000 to get the variation 
- plot errorbarplot 
- find the points outside the error bar for each judge see outliners


```{r}
library(tidyverse)
library(purrr)
library(ggplot2)
library(boot)
library(broom)
load("data/court.rda")
```

```{r}
count_video_sample <- function(dt, ){
  dt %>% 
    filter(confidence != "NA") %>%
    select(frame_id, video_id, speaker) %>% 
    group_by(video_id, speaker) %>% 
    summarise(count = n()) %>% 
    spread(speaker, count) %>% 
    rowwise() %>% 
    mutate(Total = sum(Appellent + Respondent))
}

judge_id = list("Bell","Keane","Kiefel","Gageler","Nettle","Gordon","Edelman")

df <- map(judge_id, function(judge){
  df <- au %>% filter(judge_id == judge) %>% count_video_sample() %>% filter(Total > 10)
  })

names(df) <- judge_id

sample_size <- bind_rows(df,.id = "id") %>% 
  as_tibble() %>% 
  rename(judge_id = id)

```



```{r}
au <- court %>% select(AU01_c:speaker)

au_aggregate <- au %>% 
  filter(AU01_c != "NA") %>% 
  group_by(judge_id) %>% 
  right_join(sample_size) %>% 
  summarise_at(vars(AU01_c: AU45_c), .funs = mean) %>% 
  gather(AU, mean_agg, -judge_id) 
  
  
au_video <- au %>% 
  filter(AU01_c != "NA") %>% 
  select(AU01_c: AU45_c, judge_id: speaker) %>% 
  group_by(judge_id, video_id) %>% 
  summarise_at(vars(AU01_c: AU45_c), mean) %>%
  gather(AU, mean_ind, -judge_id, -video_id) %>% 
  right_join(sample_size)

count <- au  %>% 
  select(AU01_c: AU45_c, judge_id: speaker) %>% 
  group_by(judge_id) %>% 
  right_join(sample_size) %>%
  summarise(count = n())

```

```{r}
sim_norm <- function(count, mean_true, M = 1000){
  mean <- numeric(length = M)
  for (i in seq_len(M)){
    sim <- rbinom(count, 1, mean_true)
    mean[i] <- mean(sim)
  }
  mean_sorted <- sort(mean)
  sim_mean <- mean_sorted[500] # maybe try to use qnorm()
  sim_ci_low <- mean_sorted[25]
  sim_ci_high <- mean_sorted[975]
  return(list(sim_mean = sim_mean,
              sim_ci_low = sim_ci_low,
              sim_ci_high = sim_ci_high))
}

au_sim <- au_aggregate %>% 
  left_join(count)

temp <- map2_df(.x = au_sim$count, .y = au_sim$mean_agg, 
     function(x, y) sim_norm(x, y))

au_sim2 <- au_sim %>% 
  bind_cols(temp) %>% 
  left_join(au_video, by = c("judge_id", "AU")) %>% 
  ungroup() %>% 
  mutate(outliners = as.factor(ifelse(mean_ind > sim_ci_low, 
                                      ifelse(mean_ind < sim_ci_high, 0, 1), 1)))

au_sim2 %>%
  ggplot(aes(mean_agg, AU)) + 
  geom_errorbarh(aes(xmin = sim_ci_low, xmax = sim_ci_high), col = "gray") + 
  facet_wrap(vars(judge_id)) + 
  geom_point(aes(x = mean_ind, y = AU, col = outliners))

```

```{r}
outliners <- au_sim2 %>% 
  filter(outliners == 1, mean_ind > 0.05) 

outliners %>% 
  ggplot(aes(x = mean_ind, y  =AU)) + 
  geom_point(aes(col = video_id)) + 
  facet_wrap(vars(judge_id), scales = "free_y") + 
  geom_errorbarh(aes(xmin = sim_ci_low, xmax = sim_ci_high), col = "gray")

```

- Need bootstraping for Bell and Gordon because of sample size 
- a lot of the action units are out of the simulation bound - what to do with them


notes: 
- simulation result doesnt differentiate from M = 100, 1000, 10000
- first filtered out the video with small sample - would that be a problem for bootstrapping? 

```{r}
set.seed(10000)


mean.fun <- function(data,index){
    val <-  data$value[index] 
    return(mean(val))
  }

boot_sim <- function(judge){
  
  dt <- au %>% 
    filter(judge_id ==judge, AU01_r != "NA") %>% 
    select(AU01_c : speaker) %>% 
    gather(AU, value, -c(judge_id: speaker)) %>% 
    group_by(AU) 
    
  sim <- map(split(dt,dt$AU), function(x){
    boot(x, mean.fun, R = 1000)
  })
  
  # was trying to use broom package but doesnt seem to work 
  boot_mean <- map_df(sim,function(x,y){
           t <- x$t
           sim_mean <- mean(t)
         }) %>% 
    gather(AU, boot_mean)
  
  sim_ci_low <- map_df(sim,function(x,y){
           t <- sort(x$t)
           sim_ci_low <- t[25]
         }) %>% 
    gather(AU, sim_ci_low)
  
  sim_ci_high <- map_df(sim,function(x,y){
           t <- sort(x$t)
           sim_ci_low <- t[975]
         }) %>% 
    gather(AU, sim_ci_high)
  
  boot_result <- left_join(boot_mean, sim_ci_low, by = "AU")
  boot_result <- left_join(boot_result, sim_ci_high, by = "AU")
 
  return(boot_result)
}

au_sim_bell <- boot_sim("Bell")
au_sim_gordon <- boot_sim("Gordon")



```

- get this bootstrap done TICK
- understand more about Di's thinking of modelling to deal with structural break 

