---
title: "EDA"
author: "Huize Zhang"
date: "08/04/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Read in multiple csvs with image id and face id 
```{r eval = FALSE}
judges <- c("1","2","3")

names <- map(judges, ~paste0("data/csv/face",.x, "/processed")})

filenames <- map(names, list.files, pattern = "*.csv", full.names = TRUE)

names(filenames) <- judges

temp_nauru_a <- map_df(filenames, function(x){
      map_df(x, function(x){
        read_csv(x) %>% 
          mutate(info = x) %>% 
          mutate(judge_id = as.factor(substr(x, 14,14))) %>% 
          mutate(frame_id = substr(x, 34,36))
      })
    })

temp_nauru_a_1 <- temp_nauru_a %>% select(-c(X_0 : Z_67, eye_lmk_X_0:eye_lmk_Z_55))

nauru_a <- temp_nauru_a_1 %>% 
  group_by(judge_id) %>% 
  mutate(record_id = row_number())

```

# EDA

Our judge: Justice Nettle, Justice Gageler, Justice Edelman

## Confidence

- very likely the position of the judge will affect the clarity (confidence) of the landmarking result 
- may only want to look at the observations with certain confidence 
- 0.9 as a threshold because by comparing the confidence rate with the actual face in the image, I find that when confidence is greater than 0.9, the judges are usually looking forwards. 

- Insights: Justice Nettle doesn't seem to look straight forwards very often. 
- Insights2: we may only want to use the observation with high confidence (may want to confirm the threshold)


```{r}
ggplot(nauru_a, aes(x= confidence)) +
  geom_histogram(binwidth = 0.1) + 
  facet_wrap(~judge_id)

nauru_a %>% filter(confidence >=0.9) %>% group_by(judge_id) %>% summarise(
  count = n(), 
  freq = count/148
)

high_conf <- nauru_a %>% 
  filter(confidence >= 0.9) %>% 
  mutate(indicator = as.factor(1))

ggplot(high_conf) +
  geom_point(aes(x = record_id, y = indicator))+
  facet_wrap(~judge_id, ncol = 1)

# A period that Justice Nettle (judge 1) looks up is from frame 62 to 91
# judge3: from frame 98 to 144

```

## Gaze variables 

- Gaze tracking: the vector from your pupil to corneal reflection. A bit of physio: When the light comes into your eye, you will have an relection from your outer and inner surface of your corneal and len. THe corneal relection used for gaze tracking is the reflection from the outer surface of the corneal.  
- `gaze_0_*` are for left eyes and `gaze_1_*` are for the right eyess

```{r eval =FALSE}
# statics 
p1_statics <- ggplot(nauru_a, 
             aes(x=gaze_0_x, y=gaze_0_y, colour=judge_id)) + 
  geom_point() + 
  facet_wrap(~judge_id, nrow = 3) + 
  theme(legend.position = "none")

p2_statics <- ggplot(nauru_a, 
             aes(x=gaze_1_x, y=gaze_1_y, colour=judge_id)) + 
  geom_point() +
  facet_wrap(~judge_id, nrow = 3) +
  theme(legend.position = "none")

gridExtra::grid.arrange(p1_statics, p2_statics, nrow = 1)

temp <- nauru_a %>% select(judge_id,gaze_0_x, gaze_0_y,gaze_1_x, gaze_1_y) %>% 
  mutate(x_diff = gaze_0_x - gaze_1_x,
         y_diff = gaze_0_y - gaze_1_y)

ggplot(temp) + 
  geom_histogram(aes(x = x_diff)) + 
  geom_histogram(aes(x= y_diff))
```

There's literally minor difference between the behaviour of left and right eyes - the difference in the x and y coordinates are marginal comparing to the measure of the unit. 

The scatter plot shows that Justice Nettle tends to look towards right (positive `gaze_1_x`) while the other two justices tend to look towards left. this could be because of the position where the judges sit (those who sit on the RLS tend to look towards right - look at the center)

```{r}
# animation 
p1 <- ggplot(nauru_a, 
             aes(x=gaze_0_x, y=gaze_0_y, colour=judge_id)) + 
  geom_point() + 
  facet_wrap(~judge_id, nrow = 3) +
  transition_reveal(as.numeric(frame_id)) + 
  shadow_mark() + 
  theme(legend.position = "none")

p1

# was think of having animation for both eyes side by side 
# 
# p2 <- ggplot(nauru_a, 
#              aes(x=gaze_1_x, y=gaze_1_y, colour=judge_id)) + 
#   geom_point() +
#   facet_wrap(~judge_id, nrow = 3) +
#   transition_state(as.numeric(frame_id)) + 
#   shadow_wake(wake_length = 0.5) +
#   theme(legend.position = "none")
# 
# p2
# 
# p_a <- gganimate::animate(p1, render = ffmpeg_renderer(),fps = 7)
# p2_a <- gganimate::animate(p2, render = ffmpeg_renderer(), width = 200, height = 600, fps = 7)
# 
# a_mgif <- image_read(p_a)
# b_mgif <- image_read(p2_a)
# new_gif <- image_append(c(a_mgif[1], b_mgif[1]))
# 
# for(i in 2:100){
#   combined <- image_append(c(a_mgif[i], b_mgif[i]))
#   new_gif <- c(new_gif, combined)
# }
# 
# new_gif
# anim_save("eye_track.avi", path = "animation/")

ggplot(subset(nauru_a, confidence > 0.8)) + 
  geom_point(aes(x = gaze_angle_x, y = gaze_angle_y, colour = judge_id)) +  
  geom_point(data = subset(nauru_a, between(gaze_angle_x, -0.05, 0.05) &
                             between(gaze_angle_y, -0.05, 0.05) &
                             confidence > 0.8),
             aes(x = gaze_angle_x, y = gaze_angle_y), colour = "black")+
  facet_wrap(~ judge_id)
```

## Pose

- Reflection: animation could be a good way to visualise data, especially for related high-dimensional data

- more work here to think about how to visualise it!
```{r}
scatmat(high_conf, columns = 3:5)

temp1 <- nauru_a %>% 
  select(pose_Tx, pose_Ty, judge_id, frame_id, record_id, confidence) %>% 
  mutate(signif = as.factor(ifelse(confidence > 0.9, 1, 0))) %>% 
  mutate (state = as.factor(ifelse(as.numeric(frame_id)< 60, 1,
                         ifelse(as.numeric(frame_id) > 60 & 
                                  as.numeric(frame_id) < 90, 2,3)))) 

ggplot(temp1) + 
  geom_point(aes(pose_Tx, y = pose_Ty)) + 
  facet_wrap(~judge_id) +
  transition_reveal(as.numeric(record_id)) + 
  shadow_wake(wake_length = 0.5)


ggsave("position.png", path = "images/")  
```

# face landmarking

- play around more with the animation for best visual result 

```{r eyebrow}
eyebrow <- nauru_a %>% select(judge_id, frame_id, record_id, confidence, x_17:x_26, y_17:y_26)

list <- list(paste0("y_", seq(17, 26, 1)))

eyebrow_mod <- map_df(list, function(list){
  eyebrow[list] = -eyebrow[list]
  return(eyebrow)
})

eyebrow2 <- eyebrow_mod %>% 
  gather(metrics, value, -c(judge_id, frame_id, record_id, confidence)) %>% 
  separate(metrics, c("cord", "label")) %>% 
  spread(key = cord, value = value)

ggplot(subset(eyebrow2, record_id == 1)) + 
  geom_point(aes(x = x, y = y))

ggplot(eyebrow2) + 
  geom_point(aes(x = x, y = y)) + 
  facet_wrap(~judge_id) + 
  transition_states(record_id) + 
  shadow_wake(wake_length = 0.5)

anim_save("eyebrow.mp4", path = "animation/")
```

```{r lip}
lips <- nauru_a %>% 
  select(judge_id, frame_id, record_id, confidence, x_48:x_67, y_48:y_67)

lips_list <- list(paste0("y_", seq(48, 67, 1)))

lips_mod <- map_df(lips_list, function(list){
  lips[list] = -lips[list]
  return(lips)
})

lip2 <- lips_mod %>% 
  gather(metrics, value, -c(judge_id, frame_id, record_id, confidence)) %>% 
  separate(metrics, c("cord", "label")) %>% 
  spread(key = cord, value = value)

ggplot(subset(lip2, record_id == 1)) + 
  geom_point(aes(x = x, y = y))

ggplot(lip2) + 
  geom_point(aes(x = x, y= y)) + 
  facet_wrap(~judge_id) +
  transition_states(record_id) + 
  shadow_wake(wake_length = 1)

anim_save("lip.mp4", path = "animation/")  
```


# Action Unit (Presence + Intensity)

- As indicated from the documentation (TadasBaltrusaitis/OpenFace), The AUs are more accurate in the videos than images. My results from using `FaceLandmarkImg` shows that for the intensity, which is supposed to be on a scale of 0-5 has the maximum of 3.71 for the first judge and only 4 observations has intensity greater than 3. 

```{r eval = FALSE}
au <- nauru_a %>% select(confidence, judge_id, frame_id, AU01_r:AU45_c)

# Intensity 
au_r <- au %>% select(frame_id, AU01_r:AU45_r)
au_list_r <- split(au_r, au_present$judge_id)

temp <- au_list_r[[1]]
temp %>% gather(AU, value, -c(frame_id)) %>% filter(value > 3)

# plot_r <- map(au_list_r, function(au_list){
#   au_list %>% gather(AU, value, -c(frame_id)) %>% 
#   ggplot() + 
#   geom_tile(aes(x = frame_id, y = AU, fill = value)) + 
#   theme(legend.position = "right") + 
#   scale_color_discrete()
# })
# gridExtra::grid.arrange(plot_r[[1]], plot_r[[2]], plot_r[[3]], nrow = 3)
# ggsave("intensity_of_AU.png", path = "images/")


Presence
au_present <- au %>% select(confidence, judge_id, frame_id, AU01_c:AU45_c)

au_list <- split(au_present, au_present$judge_id)

plot <- map(au_list, function(au_list){
  au_list %>% gather(AU, value, -c(confidence, judge_id, frame_id)) %>%
  ggplot() +
  geom_tile(aes(x = frame_id, y = AU, fill = as.factor(value))) +
  theme(legend.position = "right") +
  scale_color_discrete()
})

gridExtra::grid.arrange(plot[[1]], plot[[2]], plot[[3]], nrow = 3)
ggsave("presence_of_AU.png", path = "images/")



```

https://imotions.com/blog/facial-action-coding-system/

# # 2, 14, 25
# # 2, 14, 20
# # 2, 14, 25

# paper reading
Tutton, J., Mack, K., & Roach Anleu, S. (2018). Judicial Demeanor: Oral Argument in the High Court of Australia. Justice System Journal, 39(3), 273-299.

- using AV in a observational manner

- by video, such as where a judge looked (down at his or her desk, forward at the speaking barrister, across to another judge, or elsewhere in the courtroom), his or her posture (leaning forward, sitting upright, or leaning back), head or body movements (shaking or nodding the head, shrugging shoulders, or swiveling), hand movements (touching books, papers, a tablet, or parts of the face, leaning on a fist, writing, or crossing his or her arms), and interacting with other judges or an associate; 

- In the observed interactions, the judges depart from their usual appearance of detachment by: (a) displaying a helpful or supportive tone toward counsel; (b) displaying emotion; (c) using judicial humor; or (d) laughing or evoking laughter. Although these behaviors may be characterized as departures from strict norms of judicial conduct, this does not mean that they are improper or evidence of any bias. 

- Of the five occasions where emotion appeared to be clearly displayed, the most apparent judicial emotion was frustration, apparently in response to a barrister making a submission the judge appeared to regard as irrelevant.

- This judicial concern for getting to what the judge regards as the point can lead to a display of apparent frustration, especially when a barrister makes submissions on a point perceived to be irrelevant or quotes at length from material that is not thought to be relevant or helpful.


# Task week 5
- Tidy the data [mostly done] - read something on purrr & repurrrsive
  - https://jennybc.github.io/purrr-tutorial/talks.html
  - https://github.com/jennybc/repurrrsive#readme
- gganimate to see the change instead of geom_path()
- Russell will come for next Monday's meeting 

