---
knit: "bookdown::render_book"
---

\appendix

# Appendix

## List of videos used in the project

```{r results = "asis", eval = FALSE}
tibble::tibble(Case = c("The Republic of Nauru v WET040 [No. 2] [2018] HCA 60", 
                        "TTY167 v Republic of Nauru [2018] HCA 61", 
                        "Rinehart v Hancock Prospecting Pty Ltd [2019] HCA 13", 
                        "Rinehart v Hancock Prospecting Pty Ltd [2019] HCA 13", 
                        "Parkes Shire Council v South West Helicopters Pty Limited [2019] HCA 14",
                        "McKell v The Queen [2019] HCA 5",
                        "OKS v Western Australia [2019] HCA 10"), 
               Names = c("Nauru-a", "Nauru-b", "Rinehart-a", 
                         "Rinehart-b", "Parkes", "McKell", "OKS"), 
               Link = c("http://www.hcourt.gov.au/cases/cases-av/av-2018-11-07a",
                         "http://www.hcourt.gov.au/cases/cases-av/av-2018-11-07b",
                         "http://www.hcourt.gov.au/cases/cases-av/av-2018-11-13",
                         "http://www.hcourt.gov.au/cases/cases-av/av-2018-11-14a",
                         "ttp://www.hcourt.gov.au/cases/cases-av/av-2018-11-14b",
                         "http://www.hcourt.gov.au/cases/cases-av/av-2018-12-07",
                         "http://www.hcourt.gov.au/cases/cases-av/av-2019-02-14"),
               Judge = c("Nettle, Gageler, Edelman",
                         "Nettle, Gageler, Edelman",
                         "Gordon, Gageler, Bell, Keane, Edelman",
                         "Gordon, Keane, Bell, Gageler, Edelman",
                         "Gordon, Bell, Kiefel, Keane, Edelman",
                         "Gordon, Gageler, Kiefel, Nettle, Edelman",
                         "Gageler, Kiefel, Nettle, Edelman")) %>% 
  knitLatex::xTab(booktabs = TRUE, caption.top = "\\label{tab:case-info} Information on the cases used in the project")
```


|Case|Name|AV recording link|Judge|
|---|--|----|---|
|The Republic of Nauru v WET040 [No. 2] [2018] HCA 60|`Nauru_a`|http://www.hcourt.gov.au/cases/cases-av/av-2018-11-07a|Nettle, Gageler, Edelman|
|TTY167 v Republic of Nauru [2018] HCA 61|`Nauru_b`|http://www.hcourt.gov.au/cases/cases-av/av-2018-11-07b|Nettle, Gageler, Edelman|
|Rinehart v Hancock Prospecting Pty Ltd [2019] HCA 13|`Rinehart_a`|http://www.hcourt.gov.au/cases/cases-av/av-2018-11-13|Gordon, Gageler, Bell, Keane, Edelman|
|Rinehart v Hancock Prospecting Pty Ltd [2019] HCA 13|`Rinehart_b`|http://www.hcourt.gov.au/cases/cases-av/av-2018-11-14a|Gordon, Keane, Bell, Gageler, Edelman|
|Parkes Shire Council v South West Helicopters Pty Limited [2019] HCA 14|`Parkes`|http://www.hcourt.gov.au/cases/cases-av/av-2018-11-14b|Gordon, Bell, Kiefel, Keane, Edelman|
|McKell v The Queen [2019] HCA 5|`McKell`|http://www.hcourt.gov.au/cases/cases-av/av-2018-12-07|Gordon, Gageler, Kiefel, Nettle, Edelman|
|OKS v Western Australia [2019] HCA 10|`OKS`|http://www.hcourt.gov.au/cases/cases-av/av-2019-02-14|Gordon, Gageler, Kiefel, Nettle, Edelman|

Table: Details of videos processed.

## List of the name of ction units

```{r results = "asis"}

related_emotion <- c("sadness, surprise and fear",
                     "surprise, fear and interested",
                     "sadness, fear, anger and confusion",
                     "surprise, fear, anger adn interested",
                     "happiness",
                     "fear, anger and confusion", 
                     "disgust",
                     NA, 
                     "happiness and possibly contempt if appears unilateraly", 
                     "contempt or boredom if appears unilateraly", 
                     "sadness, disgust and confusion", 
                     "interested and confusion", 
                     "fear", 
                     "anger, confusion or bordom", 
                     NA, 
                     "surprise and fear", 
                     NA, 
                     NA)

au_meaning %>% 
  filter(AU_number %in% unique(au_tidy$AU)) %>% 
  rename("AU-number" = "AU_number", "AU-meaning" = "AU_meaning") %>% 
  dplyr::select(`AU-meaning`) %>% as.data.frame() %>% 
  mutate(emtion = related_emotion) %>% knitLatex::xTab(booktabs = TRUE, caption.top = "\\label{tab:au_meaning} The meaning of all the action unit estimated")
```

## Model estimation result 

```{r model_1_response, results = "asis"}
knitLatex::xTab(format(int_1, digits = 2), booktabs = TRUE, caption.top = "\\label{tab:result_1}Estimated marginal mean summary for Model 1. The confidence interval is adjusted using bonferroni adjustment")
```

```{r result-2, results = "asis"}
knitLatex::lTab(format(int_2 %>% filter(!is.na(prob)) %>% dplyr::select(-df), digits = 2), booktabs = TRUE, caption.firsthead = "model result 2 for mean presence")
```


```{r result-3, results = "asis"}
knitLatex::lTab(format(int_3 %>% filter(!is.na(prob)) %>% dplyr::select(-df), digits = 2), booktabs = TRUE, caption.firsthead = "model result 3 for mean presence")
```

```{r intensity-result-2, results = "asis"}
knitLatex::lTab(format(int_2i %>% filter(!is.na(response)) %>% dplyr::select(-df), digits = 2), booktabs = TRUE, caption.firsthead = "model result 2 for mean intensity")
```


```{r intensity-result-3, results = "asis"}
knitLatex::lTab(format(int_3i %>% filter(!is.na(response)) %>% dplyr::select(-df), digits = 2), booktabs = TRUE, caption.firsthead = "model result 3 for mean intensity")
```
