---
knit: "bookdown::render_book"
---

\appendix

# Additional stuff

## List of videos used in the project

|Case|Name|AV recording link|
|----|--|----|
|The Republic of Nauru v WET040 [No. 2] [2018] HCA 60|`Nauru_a`|http://www.hcourt.gov.au/cases/cases-av/av-2018-11-07a|
|TTY167 v Republic of Nauru [2018] HCA 61|`Nauru_b`|http://www.hcourt.gov.au/cases/cases-av/av-2018-11-07b|
|Rinehart v Hancock Prospecting Pty Ltd [2019] HCA 13|`Rinehart_a`|http://www.hcourt.gov.au/cases/cases-av/av-2018-11-13|
|Rinehart v Hancock Prospecting Pty Ltd [2019] HCA 13|`Rinehart_b`|http://www.hcourt.gov.au/cases/cases-av/av-2018-11-14a|
|Parkes Shire Council v South West Helicopters Pty Limited [2019] HCA 14|`Parkes`|http://www.hcourt.gov.au/cases/cases-av/av-2018-11-14b|
|McKell v The Queen [2019] HCA 5|`McKell`|http://www.hcourt.gov.au/cases/cases-av/av-2018-12-07|
|OKS v Western Australia [2019] HCA 10|`OKS`|http://www.hcourt.gov.au/cases/cases-av/av-2019-02-14|

Table: Details of videos processed.

## List of the name of ction units

```{r results = "asis"}
au_meaning %>% 
  filter(AU_number %in% unique(au_tidy$AU)) %>% 
  rename("AU-number" = "AU_number", "AU-meaning" = "AU_meaning") %>% 
  dplyr::select(`AU-meaning`) %>% as.data.frame() %>% 
  knitLatex::xTab(booktabs = TRUE, caption.top = "\\label{tab:au_meaning} The meaning of all the action unit estimated")
```

## Model estimation result 

```{r anova}
anova(binomial_model_1, test="Chisq") %>% kable(caption = "\\label{tab:anova}ANOVA result")
```


```{r results = "asis"}
knitLatex::lTab(format(int_2 %>% filter(!is.na(prob)) %>% dplyr::select(-df), digits = 2), booktabs = TRUE, caption.firsthead = "\\label{tab:result_2} model result 2")
```


```{r results = "asis"}
knitLatex::lTab(format(int_3 %>% filter(!is.na(prob)) %>% dplyr::select(-df), digits = 2), booktabs = TRUE, caption.firsthead = "\\label{tab:result_3} model result 3")
```

